COVID-19 Vaccine Acceptance and Hesitancy in Low and Middle Income Countries, and Implications for Messaging

### 2021-03-23 4_paper_supplementary_files/temp_download.Rmd
paper

\newpage
```{r otherv}
tab_1b
```

@@

```{r yes, results = "asis"}
tab_reasons_y
```

@@

```{r sampling}
tab_sampling
```
```{r, results = "asis"}
tab_fig1
```

@@

```{r yesall, results = "asis"}
tab_reasons_y_all
```

@@

```{r no, results = "asis"}
tab_fig2
```

@@

```{r trust, results = "asis"}
tab_trust
```
\newpage

@@

```{r, results = "asis"}
dmeans
```

@@

```{r, results = "asis"}
nas
```
________________

@@

```{r tabq1}
tab_question1
```

```{r tabq2}
tab_question2
```

```{r tabq3}
tab_question3
```

```{r tabq4}
tab_question4
```
________________

>>>>

\newpage
```{r otherv, echo=FALSE}
tab_1b
```

@@

```{r yes, results = "asis", echo=FALSE}
tab_reasons_y
```

@@

```{r sampling, echo=FALSE}
tab_sampling
```

```{r, results = "asis", echo=FALSE}
tab_fig1
```

@@

```{r yesall, results = "asis", echo=FALSE}
tab_reasons_y_all
```

@@

```{r no, results = "asis", echo=FALSE}
tab_fig2
```

@@

```{r trust, results = "asis", echo=FALSE}
tab_trust
```
\newpage

@@

```{r, results = "asis", echo=FALSE}
dmeans
```

@@

```{r, results = "asis", echo=FALSE}
nas
```
________________

@@

```{r tabq1, echo=FALSE}
tab_question1
```

```{r tabq2, echo=FALSE}
tab_question2
```

```{r tabq3, echo=FALSE}
tab_question3
```

```{r tabq4, echo=FALSE}
tab_question4
```
________________
